The process of retrieving schedule data from the Novasoftware web application

### 2016-04-18 paper/paper.tex
Edited paper, minor fix

	\section{Summary}
	%Kanske nämna något om teori-avsnittet
	%Kanske koppla lite bättre till goals
	The development of the process of extracting schedule information from the Novasoftware web application was presented, discussing problems encountered and how they were solved.

	Two major problems were to find an endpoint which information could be extracted from, as well as deciding the extraction process. This was solved by discovering the PDF image endpoint and then, through examining and experimenting with the obtained result, deriving a parsing method. The next major problem was retrieving the information that was missing from certain lessons. This was solved by finding the lesson detail page, determining the process to simulate the click as well as to extract information from the HTML result. Failing requests were managed by retrying them and performing all requests in sequence, with a timeout in between. Remarks about limitations of the described method were made, in some cases presenting methods of extension.

@@

	\section{Discussion}
	%Som någon som just ~streckläst paperet tycker jag inte instinktivt att det är repitativt. Det nämndes i början vet jag men minns inte något mer. I vilket fall som helst är det här det hör hemma som mest och borde inte tas bort.
	The data obtained using this process may be used for many applications. One example is create a custom schedule viewer with the purpose of for example increasing the availability of the information or providing a mobile friendly experience.

@@

	\subsection{Considerations}
	If you plan to implement this method please consider that the Novasoftware may get overloaded if it is receiving too many concurrent requests. If you do this, your activity will be inseparable from a DOS (Denial of Service) attack, which may damage the servers or the business. This will also limit regular users ability to use the viewer as it may slow down or restrict the availability of the application. In order to minimize the risk of slowing down or damaging the servers, please consider not sending more than one concurrent request, preferably with a timeout between each request. This is of course included in the provided implementation. It is also considerate to perform the fetching during non peak hours, such as in the night.

@@

	\newpage
	\renewcommand{\bibpreamble}{
		\textit{All sources were fetched on the date of publication of this paper. Because the information stated in the theory section (which is were the sources are referred from) of this paper is recognized as basic knowledge in the field, Wikipedia is considered a reliable source.}
	}
	\begin{thebibliography}{9}
		\bibitem{wikipedia web browser}
		Web browser - Wikipedia\\\url{https://en.wikipedia.org/wiki/Web_browser}
		\bibitem{wikipedia node.js}
		Node.js - Wikipedia\\\url{https://en.wikipedia.org/wiki/Node.js}
		\bibitem{wikipedia http request}
		Hypertext Transfer Protocol - Wikipedia\\\url{https://en.wikipedia.org/wiki/Hypertext_Transfer_Protocol}
		\bibitem{wikipedia url}
		Uniform Resource Locator - Wikipedia\\\url{https://sv.wikipedia.org/wiki/Uniform_Resource_Locator}
		\bibitem{wikipedia cookie}
		HTTP cookie - Wikipedia\\\url{https://en.wikipedia.org/wiki/HTTP_cookie}
		\bibitem{wikipedia css}
		Cascading Style Sheets - Wikipedia\\\url{https://en.wikipedia.org/wiki/Cascading_Style_Sheets}
		\bibitem{wikipedia web scraping}
		Web scraping - Wikipedia\\\url{https://en.wikipedia.org/wiki/Web_scraping}
		\bibitem{wikipedia json}
		JSON - Wikipedia\\\url{https://en.wikipedia.org/wiki/JSON}
		\bibitem{wikipedia png}
		Portable Network Graphics - Wikipedia\\\url{https://en.wikipedia.org/wiki/Portable_Network_Graphics}
		\bibitem{wikipedia pdf}
		Portable Document Format - Wikipedia\\\url{https://en.wikipedia.org/wiki/Portable_Document_Format}
		\bibitem{wikipedia regex}
		Regular expression - Wikipedia\\\url{https://en.wikipedia.org/wiki/Regular_expression}
	\end{thebibliography}
\end{document}

>>>>

	\section{Summary}
	%Kanske nämna något om teori-avsnittet
	%Kanske koppla lite bättre till goals
	The development of the process of extracting schedule information from the Novasoftware web application has been presented, discussing encountered problems and how they were solved.

	Two major problems which presented them selves during the development of the process were to find an endpoint from where information could be extracted, as well as deciding the extraction process. This was solved by discovering the PDF image endpoint and then, through examining and experimenting with the obtained results, deriving a parsing method. The next major problem was retrieving the information that was missing from certain lessons. This was solved by finding the lesson detail page and then determining the process to simulate the click as well as to extract information from the HTML result. Failing requests were managed by retrying them and performing all requests in sequence with a timeout in between. Remarks about limitations of the described method were made, in some cases presenting methods of extension.

@@

	\section{Discussion}
	%Som någon som just ~streckläst paperet tycker jag inte instinktivt att det är repitativt. Det nämndes i början vet jag men minns inte något mer. I vilket fall som helst är det här det hör hemma som mest och borde inte tas bort.
	The data obtained using this process may be used for many applications. One example is to create a custom schedule viewer with the purpose of for example increasing the availability of the information or providing a mobile friendly experience.

@@

	\subsection{Considerations}
	Anyone who plans to implement this method should consider that the Novasoftware may get overloaded if it is receiving too many concurrent requests. If not considered, the users activity will be inseparable from a DOS (Denial of Service) attack, which might damage the servers or the business. This will also limit regular users ability to use the viewer as it may slow down or restrict the availability of the application. In order to minimize the risk of slowing down or damaging the servers, one should definitely consider not sending more than one concurrent request, preferably with a timeout between each request. This is of course included in the provided implementation. It is also considerate to perform the fetching during non peak hours, such as in the night.\todo{sluta på en annan note}

@@

	\newpage
	\renewcommand{\bibpreamble}{
		\textit{All sources were reviewed at the date of publication of this paper. Because the information stated in the theory section of this paper (which is were the sources are referred from) is recognized as basic knowledge in the field, Wikipedia is considered a reliable source.}
	}
	\todo{
		Behövs inte källor, Wikipedia är bara referens
		typ av arete som inte gått ut på källforskning 	
	}

	\begin{thebibliography}{9}
		\bibitem{wikipedia web browser}
		Web browser - Wikipedia\\\url{https://en.wikipedia.org/wiki/Web_browser}
		\bibitem{wikipedia node.js}
		Node.js - Wikipedia\\\url{https://en.wikipedia.org/wiki/Node.js}
		\bibitem{wikipedia http request}
		Hypertext Transfer Protocol - Wikipedia\\\url{https://en.wikipedia.org/wiki/Hypertext_Transfer_Protocol}
		\bibitem{wikipedia url}
		Uniform Resource Locator - Wikipedia\\\url{https://sv.wikipedia.org/wiki/Uniform_Resource_Locator}
		\bibitem{wikipedia cookie}
		HTTP cookie - Wikipedia\\\url{https://en.wikipedia.org/wiki/HTTP_cookie}
		\bibitem{wikipedia css}
		Cascading Style Sheets - Wikipedia\\\url{https://en.wikipedia.org/wiki/Cascading_Style_Sheets}
		\bibitem{wikipedia web scraping}
		Web scraping - Wikipedia\\\url{https://en.wikipedia.org/wiki/Web_scraping}
		\bibitem{wikipedia json}
		JSON - Wikipedia\\\url{https://en.wikipedia.org/wiki/JSON}
		\bibitem{wikipedia png}
		Portable Network Graphics - Wikipedia\\\url{https://en.wikipedia.org/wiki/Portable_Network_Graphics}
		\bibitem{wikipedia pdf}
		Portable Document Format - Wikipedia\\\url{https://en.wikipedia.org/wiki/Portable_Document_Format}
		\bibitem{wikipedia regex}
		Regular expression - Wikipedia\\\url{https://en.wikipedia.org/wiki/Regular_expression}
	\end{thebibliography}
\end{document}
